<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# :recycle: **cache**: easily cache and retrieve computation results

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/cache)](https://CRAN.R-project.org/package=cache)
[![R-CMD-check](https://github.com/OlivierBinette/cache/workflows/R-CMD-check/badge.svg)](https://github.com/OlivierBinette/cache/actions)
<!-- badges: end -->

The **cache** package provides a simple interface to caching which works across interactive R sessions, R scripts and Rmarkdown documents. Simply wrap your R expressions with the `cache()` function to cache or retrieve the results.

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("OlivierBinette/cache")
```

## Examples

Wrap any R expression using the `cache()` function to cache the result:

```{r}
library(cache)

cache(myComputation = {Sys.sleep(3); "Hello World"})
```

The variable named `myComputation` contains the result of the computation and is available in your environment:

```{r}
print(myComputation)
```

While i,t takes 3 seconds to evaluate the expression `{Sys.sleep(3); "Hello World"}`, the previously cached result can be instantly retrieved using the same function call:

```{r}
system.time(
  cache(myComputation = {Sys.sleep(3); "Hello World"})
)

print(myComputation)
```

This is especially useful as part of a reproducible analysis workflow or as part of an Rmarkdown document. However, in constrast with the cache functionality of the `rmarkdown` package, the **cache** package can be used seamlessly across interactive sessions, reproducible analyses and Rmarkdown knitting.

## Notes

By default, the cache directory is located under a `./cache-R` folder created at the root of your project directory. This folder is located using the `here::here()` function to ensure that all project files and documents can locate it as needed.

To clear the cache and rerun all expressions, either delete the `.cache-R` folder or supply the argument `.rerun = FALSE` to the `cache()` function calls.